---
title: "ENVS-193DS Week 7 Coding Workshop"
author: "Jesse Grigolite"
date: "2023-05-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Set Up
```{r, libraries}
library(tidyverse)
library(here)
library(lterdatasampler)

library(performance)

library(broom)

library(flextable)

library(ggeffects)

library(car)
library(naniar)
```

## Linear Models

How does stem length _predict_ stem drying mass?:

```{r, filtering-data}
maples_data <- hbr_maples %>% 
  filter(year == 2003 & watershed == "Reference")
```

Visualizing missing data:

```{r, missing-data-vis}
gg_miss_var(maples_data)

```


Create exploratory visualization:

```{r, explore-data-vis}
ggplot(data = maples_data, aes(x = stem_length, y = stem_dry_mass)) +
  geom_point()
```


Let's try a model:

```{r, linear-model-maples}
#first identify y-axis, outcome,  and then predictor, x-axis
maples_model <- lm(stem_dry_mass ~ stem_length, data = maples_data)

maples_model
```

Check our assumptions:

1.) linear relationship between variables: yes! used the exploratory data visualization to check
2.) independence of errors: yes! (making assumption based on how data was collected)
3.) homoskedasticity of errors: yes! (making that decision from residuals vs. fitted plot/scale vs location plots)
4.) normally distributed errors: yes! (looking at QQ plot of residuals)

```{r, checking-assumptions}
#use plot function in console and put in your linear model to see all four plots to check assumptions
#looking at residuals plot, look homoscedastic, residuals evenly distributed
#now look at qq plot to check for normally distributed residuals, look normally distributed, follow linear path
#scale location shows same thing as first but sqrt
#look at cooks distance to check for out liars, does not look like there are out liars
#OR to display all four in the same grid, use par to set graphing parameter
par(mfrow = c(2, 2))
plot(maples_model)


```

turn off the 2 by 2 grid

```{r, turning-off-the-grid, results= FALSE}
dev.off()
```


# Putting things together to communicate

## model predictions

```{r}
# extract model predictions using ggpredict, terms correspond to the predictor in the model
predictions <- ggpredict(maples_model, terms = "stem_length")

predictions
```

plot predictions:

```{r}
plot_predictions <- ggplot(data = maples_data, aes(x = stem_length, y = stem_dry_mass))+ 
  geom_point() +
  geom_line(data = predictions, aes(x = x, y = predicted), 
            color = "blue", linewidth = 1) +
            geom_ribbon(data = predictions, aes(x = x, y = predicted,
          ymin = conf.low,  ymax = conf.high), 
              alpha = 0.2) 

plot_predictions
```


## create a table

```{r, model-summary-table}
model_summary <- summary(maples_model)

model_squares <- anova(maples_model)
model_squares

```


# making a table

```{r}
model_squares_table <- tidy(model_squares) %>% 
  mutate(p.value = case_when(
    p.value < 0.001 ~ "< 0.001"
  )) %>% 
  flextable() %>% 
  set_header_labels(df = "Degrees of Freedom", sumsq = "Sum of Squares")

model_squares_table
```

